### 2019-07-12 manuscript/main.tex
- backups of all the changes -- mainly to discussion
New Phyt style for lit cited
misc small

% New comparative approaches for the study of breeding system, polyploidy, and lineage diversification % E: the tentative title given to New Phytologist
%
% Interacting effects of ploidy and breeding system on lineage diversification % E: but "effects" is too causal
%
\begin{center}
    \textsc{Interaction between ploidy, breeding system, and lineage diversification}

@@

\noindent \textit{Keywords:} 
Polyploidy,
Breeding System,
Diversification, SSE models

@@

This work was supported by the National Science Foundation (NSF DEB-1655478 to EEG and NSF DEB-1655692 to BI).  The computing resources were provided by the Minnesota Supercomputing Institute (MSI) at the University of Minnesota.
%BI would like to thank SCHB for inspiration, sparring, and encouragement; maybe EEG, as well?

@@

\setstretch{1}
\bibliography{refs}
\bibliographystyle{evolution} % E: remove URLs
\setstretch{\stretchby}

>>>>

% Original title given to New Phytologist:
% {New comparative approaches for the study of breeding system, polyploidy, and lineage diversification} 
%
\begin{center}
    \textsc{Interaction between ploidy, breeding system, and lineage diversification}

@@

%B: added three! can have eight
\noindent \textit{Keywords:} 
Polyploidy,
Breeding Systems,
Self-incompatibility,
Diversification, 
Ploidy,
SSE models,
Diploidization.

@@

This work was supported by the National Science Foundation (NSF DEB-1655478 to EEG and NSF DEB-1655692 to BI) and the Binational Science Foundation (BSF-2016550 to IM).
The computing resources were provided by the Minnesota Supercomputing Institute (MSI) at the University of Minnesota.
%BI would like to thank SCHB for inspiration, sparring, and encouragement; maybe EEG, as well?

@@

\setstretch{1}
\bibliography{refs}
\bibliographystyle{newphytologist}
\setstretch{\stretchby}
